% ------------------------------------------------------------
\section{Calendar Week}
% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 08}
% ------------------------------------------------------------
\begin{frame}[allowframebreaks]
  \frametitle{Review CW 08}
	\begin{itemize}
		\item Experience and knowledge exchanged with O.Roffmann on 23.02.2022 regarding following Ansys topics: \textcolor{green}{Done}
		\begin{itemize}
		\item Bruno showed the Python Script created for automatization of geometry generation. Also shared a few documents with instructions of how to create such scripts in Python/SpaceClaim.
		\item Oliver showed the topic he is working on (FGM Implants) and how he approached the issue of variation of E-Modul with a "proxy-temperature" dependent material property. It is expected that this might help in diminishing the effects of stress singularity due to the interface of different materials. Very interesting approach that might be useful for our work as well.
		\item Oliver prepared a step-by-step of how to configure the RSM (Remote Solver Manager) for the MHH Ansys computing server.
		\item Bruno prepared a step-by-step of how to use the "Named Selection Worksheet" in Ansys Workbench to select ranges of nodes or elements (question from Oliver regarding Bruno's presentation in January).
		\item General exchange about relevant literature (papers, books, etc.)
		\end{itemize}
		\item Configuration of Ansys RSM performed. First test performed. It worked correctly, so that RSM can be used for future calculations involving more complicated geometries (e.g., reference from Dr. Brune) \textcolor{green}{Done}
		\item Finished chapters 8 of book "Dental Implant Prosthetics" by C. Misch (2015), covering the stress theorem for implant treatment  \textcolor{green}{Done}
	\end{itemize}
\end{frame}


% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 09}
% ------------------------------------------------------------
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Outlook CW 09}
	\begin{itemize}
		\item Continue reading in more details about bone remodelling. Start with papers from Frost, which are cited by many other researchers.
		\item During search for literature regarding bone remodelling (see above), some free available APDL scripts for education purposes from the University of Ulm and University of Sidney. Start with trying to reproduce the results of the tutorials, as it might be a good lead of how to create our own scripts.
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --

