% ------------------------------------------------------------
\section{Calendar Week}
% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 22}
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Review CW 22}
	\begin{itemize}
	\item Meeting with Prof. Dr. Stiesch and Dr. Greuling:
	\begin{itemize}
		\item On 02.06.21 at MHH
		\item Discussed about dissertation topic
		\item Details on next slide
	\end{itemize}
	\item "Dissertationsanzeige" - \textcolor{green}{Done} -> Sent for comments
	\item Translation of "Urkunden" for "Dissertationsanzeige" - \textcolor{green}{Done}
	\item "Technical setup" of softwares for project execution - \textcolor{green}{Done}:
	\begin{itemize}
		\item LaTex as text processor
		\item JabRef for literature management
		\item Python and Octave for programming
	\end{itemize}
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Review CW 22}
  	\begin{itemize}
		\item Main points of discussion about dissertation topic:
	 	\begin{itemize}
			\item Focus: Single dental implant + Peri-implant bone
			\item Geometry: Use already available geometry (from Frau Dr. 						Brune)
			\item Material: Titan (implant) + Zirkonia (Crown)
			\item Load application: Direct (no antagonist)
			\item Important: Other geometries, materials, load application methods etc. may be verified as a second step in the project.
			\item Proposal for 2nd supervisor: Prof. Dr. Junker (to be confirmed!)
			\item Conference: ICBT in November 2021. Eventually show intermediary results, if already available.
		\end{itemize}
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --
% --------------------------------------------------- Slide --
\subsection{CW 23}
% ------------------------------------------------------------
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Outlook CW 23}
  \begin{itemize}
		\item Prepare rough outline of planned dissertation -> Send for info
		\item Create first (very) simplified analytical model for implant in bone
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --

