% ------------------------------------------------------------
\section{Calendar Week}
% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 23}
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Review CW 23}
	\begin{itemize}
	\item Rough outline of planned dissertation - \textcolor{green}{Done} -> Sent for info.
	\item First (very) simplified analytical model for implant in bone - \textcolor{yellow}{Started/To be continued.}
	\item "Dissertationanzeige" - Comments implemented -> To be signed.
	\item Read article (suggestion from Dr. Greuling): Kitamura2004 / Biomechanical aspects of marginal bone resorption around osseointegrated implants... - \textcolor{green}{Done}
	\item 2nd Supervisor: Prof. Dr. Junker - \textcolor{green}{Confirmed.}
	\item Info: Parental leave from work from 15.06-14.07. Except for CW 27, more flexibility for presence at MHH.
	
	\end{itemize}
\end{frame}
% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 24}
% ------------------------------------------------------------
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Outlook CW 24}
  \begin{itemize}
		\item Continue first (very) simplified analytical model for implant in bone.
		\begin{itemize}
			\item Use dimensions from Base Model Kitamura2004 (see previous slide) as reference for our first analytical model.
		\end{itemize}
		\item Presence at MHH on Friday morning, 18.06.21. Plan: Visit to library. Eventually meeting at ZPR.
		\item Obtain "Bestaetigung der Einweisung in die Regeln guter wissenschaftlicher Praxis durch eine der Betreuungsperson". Email with instructions received from Dr. Greuling.
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --

