% ------------------------------------------------------------
\section{Calendar Week}
% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 37}
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Review CW 37}
	\begin{itemize}
		\item Work on geometry automation complete for simple geometry, bugs found have been solved (i.e., working for both the uniform as also for the elliptical damage geometry). \textcolor{green}{Done}
		\item Meeting with Dr. Greuling on 13.09.
		\begin{itemize}
			\item Points discussed regarding first results obtained:
			\begin{itemize}
				\item Concept needed of how to show the results
				\item Mesh convergence study necessary
			\end{itemize}
		\end{itemize}
	\end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Review CW 37 - Continuation}
	\begin{itemize}
		\item Points discussed regarding next steps:
		\begin{itemize}
			\item Continue to use simple geometry as for first models. More complex geometry (see work from Dr. A. Brune) to be used in a future step.
			\item Create fatigue analysis based on the model already created (i.e., including "manually" set bone reduction due to peri-implantitis)
			\item Possible results to be shown: what is the worst-case load acceptable for an implant in this simple geometry after a determined period of time (e.g., 10 years), considering the accumulated fatigue damage and the reduction of bone support in parallel.
			\item Prepare a presentation draft to show to Prof. Stiesch. Beforehand it should be discussed with Dr. Greuling to assure that the main points are covered (e.g., is the main hypothesis/question of the work clearly described?)
		\end{itemize}	
	\end{itemize}
\end{frame}

% ------------------------------------------------------------
% --------------------------------------------------- Slide --
\subsection{CW 38}
% ------------------------------------------------------------
% ------------------------------------------------------------
\begin{frame}
  \frametitle{Outlook CW 38}
	\begin{itemize}
		\item Presence planned at MHH Library on 24.09 from 10h to 12h. Participation in Workshop ("Literature research and management for Doctorate Students"). If necessary, I can show up before or after at MHH office.
		\item Perform fatigue calculation for test case (even simpler geometry at first) for titanium implant. 
	\end{itemize}
\end{frame}
% --------------------------------------------------- Slide --

